Test

### 2024-07-10 Test.Rmd
Try to merge MC and bootstrap
A consistent bootstrap method

$\mapsto$ 1

@@

>>>>

@@

# Variance théorique

```{r}
for (k in 1:nrow(trees)) {
  for (i in 1:k) {

  }
  sum_i <- sum()
}
```

# MC_boot

## Tests

```{r}
start.time <- Sys.time()

MC_boot(n = 100, B1 = 1000, B2 = 200, f = circle3_nb)
# Way too long
```

```{r}
start.time <- Sys.time()

res <- MC_boot(n = 100, B1 = 500, B2 = 100, f = circle3_nb)

end.time <- Sys.time()
time.taken1 <- end.time - start.time

time.taken1
# Way too long
```

```{r}
start.time <- Sys.time()

res <- MC_boot(n = 50, B1 = 10, B2 = 5, f = circle3_nb)

end.time <- Sys.time()
time.taken2 <- end.time - start.time

time.taken2
# Time difference of 5.522393 secs
# 31471.63 78177624.15 53692218.51
```

```{r}
start.time <- Sys.time()

res <- MC_boot(n = 100, B1 = 100, B2 = 50, f = circle3_nb)

end.time <- Sys.time()
time.taken2 <- end.time - start.time

time.taken2
# Time difference of 5.522393 secs
# 31471.63 78177624.15 53692218.51
```

# Volume

```{r}
# Total volume of trees
a <- mapply(circle3_vol, random_points[, 1], random_points[, 2], MoreArgs = list(15, 9, 6))
est_init_vol <- sum(a/p)
rm(a)
cat("Volume of the forest:", sum(trees$v), "\nEstimation of the volume of the forest:", est_init_vol)
```
